Effects of Unemployment Benefits and Uncertainty in Heterogeneous Models

### 2017-01-22 presentation/presentation.tex
Added graphs to the presentation.
Need to do the summaries
Corrected size of graph in latex
First version of summaries

  \item {1.}
  \end{itemize}
\end{frame}
\section{Part II}
\subsection{}
\begin{frame}{Welfare Measurement}
  \begin{itemize}
  \item {
  Which variable should we look at if we want to say consumers are better off? Output? Consumption?
  }
  \item {
  We want to measure somehow whether consumer welfare increased or not.
  }
  \item {
  But how to measure welfare? Can we compare the utility levels of consumers? And whose utility should we compare in a heterogeneous agent framework?
  }
  \end{itemize}
\end{frame}

\begin{frame}{Life-time Utility}
  \begin{itemize}
  \item {
  We calculate the life-time utility of each agent when the economy is in steady state. One time before the policy change and once after the policy change.
  }
  \item {
  Cannot compare two steady states directly. We need to take the transition into account.
  }
  \item {
  Calculating the exact transition path is troublesome. We follow the approximation by Krussel, Mukoyama, and Sahin (2010) which takes care of the idiosyncratic transition.
  }
  \item {
  Just place the agents in the first economy with their current assets into the second economy.
  }
  \end{itemize}
\end{frame}

@@

\begin{frame}{Consumption Equivalent}
  \centering \includegraphics[scale=5]{/cons_equiv.pdf}
\end{frame}

>>>>

  \item {1.}
  \end{itemize}
\end{frame}
\section{Part II}
\subsection{}
\begin{frame}{Welfare Analysis}
  \begin{itemize}
  \item {
  Which variable should we look at if we want to say consumers are better off? Output? Consumption?
  }
  \item {
  We want to measure somehow whether consumer welfare increased or not.
  }
  \item {
  But how to measure welfare? Can we compare the utility levels of consumers? And whose utility should we compare in a heterogeneous agent framework?
  }
  \end{itemize}
\end{frame}

\begin{frame}{Life-time Utility}
  \begin{itemize}
  \item {
  We calculate the life-time utility of each agent when the economy is in steady state. One time before the policy change and once after the policy change.
  }
  \item {
  Cannot compare two steady states directly. We need to take the transition into account.
  }
  \item {
  Calculating the exact transition path is troublesome. We follow the approximation by Krussel, Mukoyama, and Sahin (2010) which takes care of the idiosyncratic transition.
  }
  	\begin{itemize}
  	\item {
  	Just place the agents in the first economy with their current assets into the second economy.
  	}
  	\end{itemize}
  \end{itemize}
\end{frame}

@@

\begin{frame}{Consumption Equivalent}
  \centering{\includegraphics[scale=0.6]{cons_equiv}}
\end{frame}

\begin{frame}{Consumption Equivalent}
  \centering{\includegraphics[scale=0.6]{cons_equiv_unemp_emp}}
\end{frame}

\begin{frame}{Consumption Equivalent}
  \begin{itemize}
  \item {
  There exists a welfare increase in the mean and in the median.
  }
  \item {
  However, there is disagreement on whether to increase or decrease the unemployment benefits.
  }
  \item {
  Careful: the consumption equivalent is biased towards poorer agents as relative increases for them are higher than for already high-consumption agents.
  }
  \end{itemize}
\end{frame}

\begin{frame}{Cash Equivalent}
  \begin{itemize}
  \item {
  Transfer of $\Delta$ units of wealth in the first period
  }
  \end{itemize}

  \begin{equation}
  U^{2}(e,k) = U^{1}(e,k+\Delta) \nonumber
  \end{equation}

  \begin{itemize}
  \item {
  If $ \Delta>0 $ agents prefer the policy change $ (U^{2}) $, otherwise not.
  }
  \end{itemize}
\end{frame}

\begin{frame}{Cash Equivalent}
  \centering{\includegraphics[scale=0.6]{cash_equiv}}
\end{frame}

\begin{frame}{Cash Equivalent}
  \centering{\includegraphics[scale=0.6]{cash_equiv_unemp_emp}}
\end{frame}

\begin{frame}{Cash Equivalent}
  \begin{itemize}
  \item {
  There does not exist a higher welfare state in the mean, only in the median.
  }
  \item {
  If a higher welfare state existed for the mean we could redistribute wealth such that everyone would be better off. \\
  $\rightarrow$ Pareto improvement.
  }
  \item {
  One can clearly see the friction between unemployed and employed.
  }
  \end{itemize}
\end{frame}

\begin{frame}{Cash vs. Consumption Equivalent}
\centering{\includegraphics[scale=0.6]{cash_cons_equiv}}
\end{frame}

\begin{frame}{Cash vs. Consumption Equivalent}
  \begin{itemize}
  \item {
  Agents do not want full unemployment insurance although there is no moral hazard.
  }
  \item {
  Different groups in society want different policies. We did not find a policy reform that could make everyone better off.
  }
  \item {
  3
  }
  \end{itemize}
\end{frame}
